---
title: "edld610_hw2"
author: "Cameron Kay, Lea Frank, Ashley Miller"
date: "2/18/2019"
output: html_document
---

```{r setup, include = FALSE}
# load packages
library(tidyverse)
library(magrittr)
library(lubridate)
library(rio)
library(here)
library(bit64)

# load data
crime_data <- import(here("data/crime.csv"), setclass = "tibble") %>%
  janitor::clean_names() %>%
  mutate(first_occurrence_date = mdy_hms(first_occurrence_date),
         last_occurrence_date  = mdy_hms(last_occurrence_date),
         reported_date         = mdy_hms(reported_date))
```

### Part 1

Select rows corresponding to a crime and reproduce the following plot. Note that because these are proportion data, I used the following formula to calculate the standard error $\sqrt{(p(1−p)/n}$.

```{r part1_ash}

```

### Part 2

Visualize the same relation, but displaying the uncertainty using an alternative method of your choosing.

```{r part2_ash}

```

### Part 3

Reproduce the following plot. Use the reported_date to extract the year.

```{r part3_cam}

```

### Part 4

See assignment.

```{r part4_lea}

```

### Part 5

Reproduce the following table.

```{r part5_cam}

```